\documentclass[a4paper, 11pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi)
\usepackage{lipsum} %This package just generates Lorem Ipsum filler text.
\usepackage{fullpage} % changes the margin

\begin{document}
%Header-Make sure you update this information!!!!
\noindent
\large\textbf{AP Assignment} \hfill \textbf{Tan De Hui Adrian} \\
Dr Jimmy Goh \\
Due Date: 26/10/18

\section*{What was accomplished}
I successfully completed MEntry.c which is to take in and store the different values in the MEntry struct.
I was also able to accomplish dynamic hash table and complete MList.c

\section*{Difficulties}
During the assignment i faced several problems. It was mostly due to the fact that this was the first time i was doing C programming. I had no prior experience or knowledge before this in polytechnic so it was challenging.
I understood after doing extensive research that hash table was a very important part of C programming and was widely used. Initially i was not able to understand and grasp the concept of hash table. However, after consulting several friends and online materials i was more clear on how this hash table worked.

Another difficulty i faced was the memory leakage. It was sometime i had not handled in other programming languages as the other higher level languages had no need to do manual allocation of memory. This is still something that i have not been able to fully solve.

\section*{Incompleted}
Currently the only thing that i was unable to fix was the memory leakage. I was unable to make the leakage drop from a very high amount to around 19k right now with M.txt as the input file. 

\section*{What could have been done}
What could have been done in my opinion was to further understand how the memory allocation works in C programming. The bridging program was an introduciton to C programming and the topic of memory allocation was touched but in a very basic level. For this assignment i felt that i was very unsure when i would need to free and destroy. So if i could have had done more, it would be to know more on how memory allocation and freeing works.

\section*{Final Evaluation}
In summary, I learnt alot from this assignment. It gave me more insights into C programming as well as a very commonly used struct in hash table.
Majority of the stuff works but I am only left with memory allocation.




\end{document} 